% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2014 Bret A. Comnes <bac42@humboldt.edu> http://bcomnes.github.com 
% 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.}

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{
colorlinks=true,
linkcolor=blue,
urlcolor=blue
}

\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
%-----------------------------------------------------------
% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}
%-----------------------------------------------------------
% Simple footer
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[R] {\today}
\fancyfoot[C] {\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
%Feel free to adapt this for your own resume. It is certainly possible to add a bit of color if you like--I didn't want the resume to look too busy. If you'd like to add a border around the grey boxes, just change the \colorbox{mygrey} to \fcolorbox{black}{mygrey}.
\newcommand{\resheading}[1]{{\large \fcolorbox{black}{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\begin{document}

%-----------------------------------------------------------
% Header
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
	\textbf{\large Bret Comnes}  &  \\
	\textbf{Mobile:} (707) 633-4552 &  \textbf{Email:} \href{mailto:bcomnes@gmail.com}{\nolinkurl{bcomnes@gmail.com}} \\
	Portland OR & \textbf{Web:} \url{http://bret.io/} \\
\end{tabular*}
\\

\vspace{0.1in}

%-----------------------------------------------------------
% Experience
\resheading{Experience}
\begin{itemize}

%JLR
\item
\ressubheading
{Javascript Software Developer}
{July 2015 - Present}
{Jaguar Land Rover}
{Portland, OR}
\begin{itemize}
  \resitem
  {Rapid infotainment prototype development using Node.js/express.}
\end{itemize}
%Urban Airship
\item
\ressubheading
{Technical Support Engineer}
{April 2015 - July 2015}
{Urban Airship}
{Portland, OR}
\begin{itemize}
    \resitem
    {Support Urban Airships customers ranging from mobile developers to marketers.}
    \resitem
    {Custom mailing software for sending personalized emails to customers in Node.js}
\end{itemize}
%ARC Dev
\item
\ressubheading
{Web \& Systems Developer}
{May 2014 - April 2015}
{PSU Office of Information Technology - Academic \& Research Computing}
{Portland, OR}
\begin{itemize}
    \resitem
    {Web applications and systems programming with Python and Django.}
    \resitem
    {Implemented and designed a Github style email correspondence bridge for ARCs ticketing system.}
    \resitem
    {Implemented user tracking and notification system for ARC's research systems.}
    \resitem
    {Writing package that tracks MySQL and Postgres database activity of ARCs hosted projects.}
\end{itemize}

%ARC Ops
\item
\ressubheading
{Systems Administrator}
{May 2013 - April 2015}
{PSU Office of Information Technology - Academic \& Research Computing}
{Portland, OR}
\begin{itemize}
    \resitem
    {Responsible for building, automating and monitoring PSU's research servers and Linux Clusters.}
    \resitem
    {Initiated efforts to automate cluster deployment and management using configuration management.}
    \resitem
    {Launched a successful user support documentation website to orient new users on the available research systems.}
    \resitem
    {Trained and introduced new users to ARCs resources and shared unix computing environments.}
\end{itemize}

% Erik's Lab
\item
\ressubheading
{Research Assistant to Dr. Erik Sanchez}
{May 2013 - April 2015}
{PSU S\'anchez Nano Development Lab}
{Portland, OR}
\begin{itemize}
    \resitem
    {Wrote custom control software and a web application that enabled remote viewing and operation of a Scanning Electron Microscope over the internet using Web Sockets and WebRTC.}
\end{itemize}

% Teachers Assistant
\item
\ressubheading
{Lab Instructor \& Teachers Assistant}
{September 2012 - December 2014}
{Portland State University}
{Portland, OR}
\begin{itemize}
	\resitem
    {Instructed PSU's General Physics Labs and assisted in the upper division Experimental Physics Labs.}
	\resitem
    {Developed two novel labs on the use of microcontrollers and FPGAs covering basic concepts to advanced topics like PID control theory.}
\end{itemize}

% Textbook Consultant
\item
\ressubheading{Textbook Development Consultant}{January 2012 - July 2012}{Cardinal TS}{Remote in Ashland, OR}
\begin{itemize}
    \resitem
    {Front end Javascript development for a interactive calculus textbook website for Wiley Publishing.}
	\resitem
    {Provided conceptual content and calculus interpretation for other members of the development team.}
\end{itemize}

% Gravlab
\item
\ressubheading
{Research Assistant to Dr.\ C\@.D.\ Hoyle}
{May 2009 - September 2011}
{HSU Gravitational Research Laboratory}
{Arcata, CA}
\begin{itemize}
    \resitem
    {Designed and machined custom experimental instruments and developed the lab's data collection, automation and analysis software to study the gravitational inverse-square law at sub-millimeter distance scales.}
\end{itemize}

% Arecibo
\item
\ressubheading
{Research Assistant to Dr.\ David Kornreich}
{November 2009}
{The Arecibo Legacy Fast ALFA Survey}
{Arecibo, Puerto Rico}
\begin{itemize}
    \resitem
    {Trained and operated one of the worlds largest radio telescopes and analyzed the collected data searching for previously undiscovered galaxies.}
\end{itemize}

%% Grading
%\item
%\ressubheading
%{Academic Assistant}
%{January 2009 - May 2011}
%{Humboldt State University}
%{Arcata, CA}
%\begin{itemize}
%    \resitem{Graded student homework and lab write-ups for an introductory electronics course for $\sim$60 undergraduate physics and engineering students.}
%\end{itemize}

\end{itemize}

\pagebreak[4]

%-----------------------------------------------------------
% Education
\resheading{Education}
\begin{itemize}
% PSU
\item
\ressubheading
{Masters in Applied Physics}
{September 2012 - April 2015}
{Portland State University}
{(On leave) Portland, OR}	

% HSU
\item
\ressubheading
{Bachelor of Science in Physics}
{August 2006 - May 2011}
{Humboldt State University}
{Arcata, CA}
\end{itemize}

%-----------------------------------------------------------
% Skills
\resheading{Skills}

\begin{description}
% Languages
\item[Operating Systems, Languages, \& Applications]\-
\begin{itemize}
    \resitem
    {\textbf{Fluent:} Linux/Unix, OS X, Windows, Node flavored Javascript, Python, Git/Github, HTML, CSS, Ansible, systemd, Mathematica}
    \resitem
    {\textbf{Familiar:} Go, Ruby, electron, bash, *SQL, C/autotools, regex, LevelDB, backbone.js, websockets, WebRTC, Oauth}
\end{itemize}

% Miscellaneous
\item[Character:]
Demonstrated proficiency with public communication skills.  Exceptional troubleshooting and debugging skills.  Adept at rapidly learning new programming languages and tools. Expert at remote/distributed collaboration and open source development. Excels at teaching and learning with others.  Goal driven.  Positive.

\end{description}


%-----------------------------------------------------------
% Publications
\resheading{Publications, Talks, Community Involvement \& Leadership}
\begin{itemize}
\item
\ressubheading
{PDX Node}
{September 2015 - Present}
{Organizer \& Volunteer}
{}
	
% Social WG
%\item
%\ressubheading
%{W3C Social Web Working Group}
%{July 2014 - June 2015}
%{Invited Expert}
%{}

% Code for portland
\item
\ressubheading
{Code for Portland}
{March 2014 - July 2015}
{Organizer \& Volunteer}
{}

% UO WebRTC thint
%\item
%\ressubheading
%{``Development of an Online Teaching Field Emission SEM''}
%{February 2014}
%{Proceedings of the Oregon Academy of Science}
%{}

% Homebrew Websi te Club
%\item
%\ressubheading
%{Homebrew Website Club}
%{December 2013 - July 2015}
%{Organizer}
%{}

% Puppet
%
%\item
%\ressubheading
%{Bug Triage-A-Thon}
%{October 2013}
%{Puppet Labs}
%{}

% WebRTC Camp
\item
\ressubheading
{``Remote Operation of a Scanning Electron Microscope using WebRTC''}
{October 2013}
{WebRTC Camp}
{}

% OSFW3C
\item
\ressubheading
{``Distributed Social Web Interactions with Semi-Static Websites''}
{August 2013}
{OSFW3C Workshop on Social Standards: The Future of Business}
{}

% IndieWeb
%\item
%\ressubheading
%{IndieWebCamp}
%{2013,2014,2015 - Present}
%{Participant and Organizer}
%{}

% MFS
%\item
%\ressubheading
%{PSU Manufacturing and Fabrication for the Sciences Club}
%{2013 - December 2014}
%{Officer}
%{}

% NCUR Paper
%\item
%\ressubheading
%{``Sub-millimeter Positioning and Sensing for Short-Range %Gravity Tests"}
%{2011}
%{Proceedings of the 25th National Conference on Undergraduate Research (NCUR)}
%{}

% HSU Talk
%%\item
%%\ressubheading
%%{``Studying the Weak Equivalence Principal Below 50 Microns"}
%%{2011}
%%{Humboldt State University Physics Seminar}
%%{}
\end{itemize}

%-----------------------------------------------------------
% Open Source
\resheading{Recent Open Source Contributions}
\begin{itemize}
% node learnbook
\item
\ressubheading
{Node Learnbook}
{E-Book}
{\href{https://github.com/bcomnes/node-learnbook}{github.com/bcomnes/node-learnbook}}
{io.js gurus approve!}
\begin{itemize}
\resitem
{A book about how and where to learn about node and javascript}
\end{itemize}
% standard format
\item
\ressubheading
{standard-format}
%{2013 - 2014}
{Node.js}
{\href{https://www.npmjs.com/package/standard-format}{npmjs.com/standard-format}}
{$\sim38\,000+$ downloads/month}
\begin{itemize}
    \resitem{Automatically format javascript to conform to \href{https://www.npmjs.com/package/standard}{standard} Javascript Styling rules.}
\end{itemize}

% sublime standard format
\item
\ressubheading
{Sublime StandardFormat}
%{2013 - 2014}
{Python}
{\href{https://packagecontrol.io/packages/StandardFormat}{packagecontrol.io/packages/StandardFormat}}
{$\sim550+$ downloads/month}
\begin{itemize}
    \resitem{A Sublime Text plugin to autoformat javascript to conform to standard on file save.}
\end{itemize}

% twitter-video
\item
\ressubheading
{twitter-video}
{Node.js}
{\href{https://www.npmjs.com/package/twitter-video}{https://www.npmjs.com/package/twitter-video}}
{tweeps approved!}
\begin{itemize}
\resitem
{A small module and cli for uploading video to twitters api}
\end{itemize}

%aredridel/homebrew-iojs
\item
\ressubheading
{homebrew-iojs}
{Ruby}
{\href{https://github.com/aredridel/homebrew-iojs}{https://github.com/aredridel/homebrew-iojs}}
{down with barriers to publishing!}
\begin{itemize}
\resitem
{Help maintain a homebrew tap for installing working versions of node/iojs and npm}
\end{itemize}

\end{itemize}
\begin{description}
\item[Github:] See \url{https://github.com/bcomnes} for more contributions
\end{description}

%-----------------------------------------------------------
% End

\end{document}
